### 2015-02-11 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added new plots used in hose report, updated the report, and added new script to plot/analyze BDP data for specific hose streams

% Load packages
\usepackage{graphicx}

@@

\section{Experimental Structure}
\label{sec:Experimental_Structure}

@@

\subsection{Water Flow Experimental Procedure}
\label{sec:Water_Flow_Procedure}
A total of four sets of experiments were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.

Two sets of experiments involving application patterns, Tests 18 and 19, were conducted. The two sets varied in that the first floor south side door was open for Test 18 (Fig.~\ref{fig:test_18_plan}) and closed for Test 19 (Fig.~\ref{fig:test_19_plan}).

Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the first floor, south side double doors using a 1.75 in. hose with a combination nozzle. The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure first and second floor layouts for Test 18]{West Structure first floor (top) and second floor (bottom) layouts for Test 18. Both double doors and the south side door were open on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:test_18_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19. Both double doors were open and the south side door was closed on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:test_19_plan}
\end{figure}

@@

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of North Double Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of North Double Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
\end{figure}

>>>>

% Load packages
\usepackage{graphicx}
\usepackage[super]{nth}

@@

\section{Experimental Structure}
\label{sec:Experimental_Structure}
This series of field experiments was conducted at the Delaware County Emergency Services Training Center in Sharon Hill, PA.

Two concrete structures were built on a concrete slab as shown in Figure XX. They were designed to simulate a single story and a two story residential structure.  The first floor of each structure had an outer wall composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long. The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

The interior walls of the first floor or each structure were framed with steel studs and track.  The studs were set to 0.40 m (16 in) centers.  The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.  The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure  XX .  Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed (nailed?) to the top of the TJIs.

The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs etc…

Opening front door, window, rear doors.

Single story  
The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed “floor assembly”.  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

@@

\subsection{Water Flow Experimental Procedure}
\label{sec:Water_Flow_Procedure}

\subsubsection{East Structure Experiments}
\label{sec:East_Structure_Water_Flow_Procedure}

\subsubsection{West Structure Experiments}
\label{sec:West_Structure_Water_Flow_Procedure}

Four sets of water flow experiments were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure. Water was flowed from the double doors on the first floor for all experiments. The experiments varied based on flow path configurations and the type of nozzle used. Two flow path configurations were used. Both configurations contained the double doors on the first level in the opened position and the stairwell door and west side double door on the second level being opened and closed depending on the time in the experiment. The main difference between the two configurations was that the first level, south side door was in the opened position for Flow Path Configuration 1 and was in the closed position for Flow Path Configuration 2. Fig.~\ref{fig:flow_path_1} and Fig.~\ref{fig:flow_path_2} contain the floor plan schematics for Flow Path Configuration 1 and Flow Path Configuration 2, respectively.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption[Flow path configuration used during West Structure water flow experiments]{West Structure first floor (top) and second floor (bottom) layouts for Test 18. Both double doors and the south side door were open on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19. Both double doors were open and the south side door was closed on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}

The four sets of water flow experiments conducted in the West Structure contained two different procedures for each flow path configuration. One of the procedures involved using a monitor nozzle to flow water at fixed positions in the first floor of the structure, and the other procedure used a handline equipped with a combination nozzle to flow water into the first floor of the structure in various application patterns.  The second procedure used a 1$\frac{3}{4}$" handline equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern. Each stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.

\subsubsection{Monitor Nozzle Experimental Procedure}
\label{sec:Monitor_Procedure}
Two sets of the experiments, Tests 16 and 17, involved flowing water from a monitor nozzle in a straight stream, narrow fog stream, and wide fog stream pattern. Each stream was aimed at two different locations on the first floor interior ceiling: the "far target", which was located approximately X m (Xft) from the south interior wall, and the "near target" which was located approximately X m (Xft) from the interior wall of the double doors.

\subsubsection{Handline Experimental Procedure}
\label{sec:Handline_Procedure}
Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1$\frac{3}{4}$" handline equipped with a combination nozzle. Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.

Tests 18 and 19 followed identical procedures that involved flowing water from a handline using different hose stream and application pattern combination.  The handline combination nozzle was adjusted to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

@@

@@

Significant air flow through the stairwell and \nth{2} level double door only occurred when the flow path was complete, or when both doors were in the open position. Tables~\ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} contain the average air velocity measured by the eight BDPs at the stairwell door and \nth{2} level, double door, respectively, during the time the flow path was complete for each application pattern and hose stream combination used during Tests 18 and 19.

\begin{table}[!ht]
\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
\begin{tabular}{|l|l|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Test 18} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.17 & 0.48 & 0.65 & 0.63 \\ \hline
\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 \\ \hline
\textit{Wide Fog} & 0.93 & 0.90 & 0.91 & 0.75 \\ \hline
\multicolumn{5}{|c|}{Test 19} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
\textit{Narrow Fog} & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
\textit{Wide Fog} & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Test 18} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.43 & 1.75 & 2.46 & 2.40 \\ \hline
\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 \\ \hline
\textit{Wide Fog} & 3.02 & 3.22 & 3.06 & 2.57 \\ \hline
\multicolumn{5}{|c|}{Test 19} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
\textit{Narrow Fog} & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
\textit{Wide Fog} & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A13_Avgs}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
\end{figure}
